Beyond Adaptive Web Design

### 2014-03-16 paper/paper.tex
refactor: restyle sentences

\begin{abstract}
Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also high-latency networks. But there are not just smartphones and desktop computers. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. So it is necessary to adapt web pages for different devices and new interaction methods. Several new methods for designing web are rapidly evolving. We present a new way of web components adaptation based on a device features and external conditions in our work and new possibilities of interaction with web application based on speech recognition, motion or device rotation.
\end{abstract}

@@

We consider ``adaptive web design'' as an equal with creating a single Web experience that adjusts based on the capabilities of the device and browser. Website can access sensors in devices and use them to enhance user experience.

@@

The best touch interface is sometimes no touch at all. We can use sensors and speech input which is the next frontier for interaction design.

@@

From controlling the user interface based on three dimensional motion as input, to combining device motion with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}. There is a lot of interesting interface designs made possible by Device Motion. It depends on us how we use them.

@@

This approach works quite well for simple use cases. We can show multiple map types, markers or videos. However, more interactive elements require additional consideration. Even then use of an embedded elements directly still might not make sense because of unnecessary traffic, while adaptive techniques reduces it. We can still replace basic static image with richer elements.

>>>>

\begin{abstract}
Mobile device penetration grows rapidly and it brings not only different display sizes with new human interaction methods, but also high-latency networks. But there are not just smartphones and desktop computers. We now have Web-enabled smartphones, tablets, e-readers, netbooks, watches, TVs, phablets, notebooks, game consoles, cars and more. So it is necessary to adapt web pages for different devices and new interaction methods. Several new methods for designing web are rapidly evolving. We present a new way of web components adaptation based on a device features and external conditions in our work. We introduce new possibilities of interaction with the web applications based on speech recognition, motion or device rotation.
\end{abstract}

@@

We consider ``adaptive web design'' as an equal with creating a single Web experience. We can adjust it based on the capabilities of the device and browser. Website can access sensors in devices and use them to enhance user experience.

@@

The best interface can be sometimes controlled without touching at all. We can use sensors and speech input which is the next frontier for interaction design.

@@

We can control the user interface based on three dimensional motion as input or we can combine it with another sensors as are location detection or video cameras~\cite{AccelerationAndGyroscope}. There are a lot of interesting interface designs made possible by device motion. It depends on us how we use them.

@@

This approach works quite well for simple use cases. We can show multiple map types, markers or videos. However, more interactive elements require additional consideration. Even then use of an embedded elements directly still might not make sense because of unnecessary traffic. We can still use adaptive techniques to reduce it and replace basic static image with richer elements.
